### 2023-09-05 3.Design/activation.tex
added memcell part, to finsih

Activation functions play a great role in the results obtained \cite{af}. It is the reason why making good Activation function circuits is fundamental. Of course the easy way would be to simply design a hard sigmoid ($h(x)=max(0,min(1,\frac{x+1}{2}))$), the issue being that the hard sigmoid is much worse than the regular sigmoid, especially for regression problems \cite{hardSigm}.

@@

Due to the nature of the functions we want to generate, we will use the same circuit for both a sigmoid and a hyperbolic tangent like functions. The two different functions are generated by changing two parameters.

>>>>

Activation functions play a great role in the results obtained \cite{af}. It is the reason why making good Activation function circuits is fundamental. Of course the easy way would be to simply design a hard sigmoid ($h(x)=max(0,min(1,\frac{x+1}{2}))$), the issue being that the hard sigmoid is much worse than the regular sigmoid, especially for regression problems \cite{hardSigm}. The same goes for the \ac{tanh} and hard \ac{tanh} functions.

@@

Due to the nature of the functions we want to generate, we will use the same circuit for both a sigmoid and a \ac{tanh} like functions. The two different functions are generated by changing two parameters.
